\thispagestyle{empty}

\setcounter{page}{2}

\subsection*{About This Document}

%\subsection*{Preliminary Release Note}

The {\bfseries \chipname{} \GetTranslation{doctype}} is targeted at developers working on low level software projects that use the \chipname{} SoC. It describes the hardware modules listed below for the \chipname{} SoC and other products in \chipname{} series. The modules detailed in this document provide an overview, list of features, hardware architecture details, any necessary programming procedures, as well as register descriptions.

\subsection*{Navigation in This Document}
Here are some tips on navigation through this extensive document:
\begin{itemize}
    \item \hyperref[tab:release-status]{Release Status at a Glance} on the very next page is a minimal list of all chapters from where you can directly jump to a specific chapter.
    \item Use the \textbf{Bookmarks} on the side bar to jump to any specific chapters or sections from anywhere in the document. Note this PDF document is configured to automatically display \textbf{Bookmarks} when open, which is necessary for an extensive document like this one. However, some PDF viewers or browsers ignore this setting, so if you don't see the \textbf{Bookmarks} by default, try one or more of the following methods:
    \begin{itemize}
        \item Install a PDF Reader Extension for your browser;
        \item Download this document, and view it with your local PDF viewer;
        \item Set your PDF viewer to always automatically display the \textbf{Bookmarks} on the left side bar when open.
    \end{itemize}
    \item Use the native \textbf{Navigation} function of your PDF viewer to navigate through the documents. Most PDF viewers support to go \textbf{Up}, \textbf{Down}, \textbf{Previous}, \textbf{Next}, \textbf{Back}, \textbf{Forward} and
    \textbf{Page} with buttons, menu, or hot keys.
    \item You can also use the built-in \textbf{GoBack} button on the upper right corner on each and every page to go back to the previous place before you click a link within the document. Note this feature may only work with some Acrobat-specific PDF viewers (for example, Acrobat Reader and Adobe DC) and browsers with built-in Acrobat-specific PDF viewers or extensions (for example, Firefox).
\end{itemize}
